---
title: "Satish_SVAP_Asmt"
author: "Satish Kaushik"
date: "7/15/2017"
output:
  html_document: default
  pdf_document: default
---

# Frame and Acquisition of Data
I have choosen to scrape data from NHRFD on a Day basis. Collected 5 years data from year 2012 to year 2016.

```{r}
library(rvest)
pg.out = read_html('../MonthWiseMarketArrivals_Potato.html')
pg.table = pg.out %>%
           html_node('#dnn_ctr974_MonthWiseMarketArrivals_GridView1') %>%
           html_table()
df = pg.table
str(df)
```

# Refine
- Rename the column names
```{r}
newnames = c('market', 'month', 'year', 'quantity', 'priceMin', 'priceMax', 'priceMod' )
colnames(df) = newnames
str(df)
```

- Remove last row which contains Total details.
```{r}
library(dplyr)
tail(df)
df = df %>%
  filter(year != "Total")
tail(df)
```

- Change the respective data types

```{r}
df$year = as.numeric(df$year)
df$priceMin = as.numeric(df$priceMin)
df$priceMax = as.numeric(df$priceMax)
df$priceMod = as.numeric(df$priceMod)
str(df)
```

- Create the date column
```{r}
head(df)
df = df %>% 
  mutate(date = paste("01", month, year, sep="-"))
df$date = as.Date(df$date, "%d-%B-%Y")
str(df)
```

- Split City/State Names from market column

```{r}
library(stringr)
library(tidyr)
df = df %>% 
  mutate(market1 = market) %>%
  separate(market1, c('city', 'state'), sep = "\\(")
head(df, 20)
```

# Analyzing the data using plots/graphs
- Plot of month vs quantity, different colors for each year
```{r}
library(ggplot2)

g1 = ggplot(df) + 
  aes(df$month, df$quantity, color=year) + 
  geom_point()
g1
```

- plot of month vs max price, different colors for each year
```{r}
g2 = ggplot(df) + 
  aes(df$month, df$priceMax, color=year) + 
  geom_point()
g2
```


```{r}
library(plotly)
ggplotly(g1)
```
#interactive visualization of data

```{r}
library(crosstalk)
library(d3scatter)

shared_rawdata <- SharedData$new(df)

bscols(
  list(
    filter_checkbox("month", "monthSelect", shared_rawdata, ~month, inline = TRUE),
    filter_checkbox("year", "yearSelect", shared_rawdata, ~year, inline = TRUE),
    filter_slider("Quantity", "Quantity", shared_rawdata, ~quantity, width = "100%")
  ),
  
  d3scatter(shared_rawdata, ~year, ~quantity, ~year, width="100%", height=300),
  d3scatter(shared_rawdata, ~year, ~quantity, ~month, width="100%", height=300)

)
```

